Jackson Strand

### 2024-03-20 index.qmd
commit for 3/20

```{=html}
<div  style="margin: 30px; text-align: center;">
  <a class="btn btn-primary" href="cv.qmd" role="button" style="padding: 15px 30px;">View my CV</a>
</div>
```

>>>>

```{=html}
<div  style="margin: 30px; text-align: center;">
  <a class="btn btn-primary" href="qmd/cv.qmd" role="button" style="padding: 15px 30px;">View my CV</a>
</div>
```
